---
title: "README"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# [MODA: An R package for Bayesian Variable Selection using Orthogonal Data Augmentation](https://github.com/merliseclyde/MODA)

The Modal Orthogonal Data Augmentation Package or `MODA` finds posterior modes of the model space under generalized ridge shrinkage priors with a point mass at zero.  In addtion to finding modes, the algorithms provide an exploration of high posterior probability models.


Some CRAN statistics: [![](http://cranlogs.r-pkg.org/badges/MODA)](http://cran.rstudio.com/web/packages/MODA/index.html) [![](http://cranlogs.r-pkg.org/badges/grand-total/MODA)](http://cran.rstudio.com/web/packages/MODA/index.html)

On the other hand, we welcome everyone to use the most recent version
of the package with quick-fixes, new features and probably new
bugs. It's currently hosted on
[GitHub](https://github.com/merliseclyde/MODA). To get the latest
development version from [GitHub](https://github.com/merliseclyde),
use the `devtools` package from
[CRAN](https://cran.r-project.org/package=devtools) and enter in `R`:

```{r}
# library(devtools)
# install_github("merliseclyde/MODA")
```



